Supplementary material

### 2018-08-18 sup/sup.tex
online documenttion included
better order

\documentclass[a4paper]{article}  
\usepackage{url}
\usepackage{hyperref}
\usepackage{multirow}
\title{Supplementary material}
\author{}
\date{}
\ifpdf%                                % if we use pdflatex
  \pdfoutput=1\relax                   % create PDFs from pdfLaTeX
  \pdfcompresslevel=9                  % PDF Compression
  \pdfoptionpdfminorversion=7          % create PDF 1.7
  \ExecuteOptions{pdftex}
  \usepackage{graphicx}                % allow us to embed graphics files
  \DeclareGraphicsExtensions{.pdf,.png,.jpg,.jpeg} % for pdflatex we expect .pdf, .png, or .jpg files
\else%                                 % else we use pure latex
  \ExecuteOptions{dvips}
  \usepackage{graphicx}                % allow us to embed graphics files
  \DeclareGraphicsExtensions{.eps}     % for pure latex we expect eps files
\fi%
\graphicspath{{figures/}{pictures/}{images/}{./}} % where to search for the images

@@

\section{Expert comments}

\subsection{Original request}
As part of our efforts in the Urban Genome Project of the University of Toronto,
we are trying to build infrastructure to help understand recurrent and
distinctive patterns of urban change.

@@

\subsection{A - Cary Wu}
%\href{https://soci.ubc.ca/persons/cary-wu/}{\url{https://soci.ubc.ca/persons/cary-wu/}}
\emph{Doctoral candidate in Sociology at the University of British Columbia, Canada.}

@@

>>>>

\documentclass[a4paper]{article}  
\usepackage{url}
\usepackage{hyperref}
\usepackage{multirow}
\usepackage[final]{pdfpages}

\title{Supplementary material}
\author{}
\date{}
\ifpdf%                                % if we use pdflatex
  \pdfoutput=1\relax                   % create PDFs from pdfLaTeX
  \pdfcompresslevel=9                  % PDF Compression
  \pdfoptionpdfminorversion=7          % create PDF 1.7
  \ExecuteOptions{pdftex}
  \usepackage{graphicx}                % allow us to embed graphics files
  \DeclareGraphicsExtensions{.pdf,.png,.jpg,.jpeg} % for pdflatex we expect .pdf, .png, or .jpg files
\else%                                 % else we use pure latex
  \ExecuteOptions{dvips}
  \usepackage{graphicx}                % allow us to embed graphics files
  \DeclareGraphicsExtensions{.eps}     % for pure latex we expect eps files
\fi%
\graphicspath{{figures/}{pictures/}{images/}{./}} % where to search for the images

@@

\section{Original request for feedback}
As part of our efforts in the Urban Genome Project of the University of Toronto,
we are trying to build infrastructure to help understand recurrent and
distinctive patterns of urban change.

@@

\section{Documentation}
\includepdf[pages=-,pagecommand={},width=1.5\textwidth]{Documentation.pdf}

\section{Expert comments}
\subsection{A - Cary Wu}
%\href{https://soci.ubc.ca/persons/cary-wu/}{\url{https://soci.ubc.ca/persons/cary-wu/}}
\emph{Doctoral candidate in Sociology at the University of British Columbia, Canada.}

@@

% \end{document}
